---
title: "DataViz"
authors: "gmo"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: flatly
    source_code: embed
---


```{r}
library(tidyverse)
library(flexdashboard)
library(gmo)

```


# Home {data-icon='fa-home'}

<h3><u> A taxonomy of visualization tools: </u></h3>

Exploratory Data Analysis (EDA) is a fundamental step in Data Science.
<br>
<br>
Whether the goal is to understand, investigate, or communicate insights, EDA plays a crucial role.
<br>
<br>
That’s why it’s important <b> to be familiar </b> with the different types of data visualizations available.


# Pie Chart {data-navmenu="Proportions"}

# Donut Chart {data-navmenu="Proportions"}

# Treemap {data-navmenu="Proportions"}

# Stacked Bar Chart {data-navmenu="Proportions"}

# Stacked Area Chart {data-navmenu="Proportions"}

# Bubble Chart {data-navmenu="Relationships"}

# Histogram {data-navmenu="Relationships"}


```{r}
gmo_product %>% 
  gmo_chart_distribution(feature = Formula,values = APAP.Assay,vertical = 0,overlap = 0.9,title = "Histogram",lab_x = "Value (%)",lab_y = "Products")

```

# Force-Directed Graph {data-navmenu="Relationships"}

# Chord Diagram {data-navmenu="Relationships"}

# Scatter Plot {data-navmenu="Relationships"}

```{r}
gmo_product %>% 
  gmo_chart_barpoint(feature = Formula,values = APAP.Assay,vertical = 0,title = "Barpoint",lab_x = "Value (%)",lab_y = "Products")

```



# Correlation Matrix {data-navmenu="Relationships"}

# Stem-and-leaf {data-navmenu="Relationships"}

# Headmap {data-navmenu="Difference"}

# Radar Chart {data-navmenu="Difference"}

# Star Plot {data-navmenu="Difference"}

# Parallel Coordinates Plot {data-navmenu="Difference"}

# Bubble Map {data-navmenu="Spatial"}

# Flow Map {data-navmenu="Spatial"}

# Choropleth {data-navmenu="Spatial"}



